Biofouling

### 2023-06-10 smelt_2019_allseasons/Biofouling.Rmd
prep data

---
title: "Biofouling"
author: "Nicole Kwan"
date: "2023-06-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

---
title: "Biofouling"
author: "Nicole Kwan"
date: "2023-06-09"
output: html_document
editor_options: 
  chunk_output_type: console
---

# load packages
```{r message=FALSE, warning=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
library(tidyverse)
```

# bring in & prep data
```{r}
biofoul <- read_csv("smelt_2019_allseasons/data_raw/Invert.data.csv")
diet <- read_csv("smelt_2019_allseasons/data_clean/Diet.proportions.csv")
zoop <- read_csv("smelt_2019_allseasons/data_clean/Zoop.catch.csv")

#unique(prop2$Taxa)
#unique(caught.19$Taxa)
#unique(biofoul$Taxa)

#filter diet dataset to just fall fish
diet.fall <- filter(diet, Season == "Fall")

#filter zoop dataset to final day of sampling 
zoop.fall <- filter(zoop, Date == "2019-11-04")

#match up taxa names to work with biofoul data
zoop.fall$Taxa2 <- zoop.fall$Taxa
zoop.fall[zoop.fall$Taxa %in% c("Cyclopoid", "Calanoid"),]$Taxa2 <- "Copepod"
zoop.fall[zoop.fall$Taxa %in% c("Microzoo", "Ostracod", "Cladocera"),]$Taxa2 <- "Other"

diet.fall$Taxa2 <- diet.fall$Taxa
diet.fall[diet.fall$Taxa %in% c("Cyclopoid", "Calanoid"),]$Taxa2 <- "Copepod"
diet.fall[diet.fall$Taxa %in% c("Ostracod", "Cladocera"),]$Taxa2 <- "Other"

biofoul$Taxa2 <- biofoul$Taxa
biofoul[biofoul$Taxa %in% c("Corphiidae", "Gammaridae"),]$Taxa2 <- "Amphipod"

#condense
zoop.fall2 <- zoop.fall[c(1,10,7)]
diet.fall2 <- diet.fall[c(2,5,3)]
biofoul2 <- biofoul[c(1,4,3)]

#rename columns
zoop.fall2 <- zoop.fall2 %>% rename(zoop = "ind_m3")
diet.fall2 <- diet.fall2 %>% rename(diet = "prop.mean")
biofoul2 <- biofoul2 %>% rename(biofoul = "Count")

#combine
all <- merge(zoop.fall2, diet.fall2, by="Location")
```

# plot
```{r}

```
